---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mreg

<!-- badges: start -->
[![R-CMD-check](https://github.com/shug0131/mreg/workflows/R-CMD-check/badge.svg)](https://github.com/shug0131/mreg/actions)
[![Codecov eudract_pkg](https://codecov.io/gh/shug0131/mreg/branch/master/graph/badge.svg)](https://app.codecov.io/gh/shug0131/mreg?branch=master)

<!-- badges: end -->

The goal of mreg is to implements the techniques of exact likelihood when the discrete outcome can be missing in a regression model. It is the accompanying software to the paper Bond S, Farewell V, 2006, Exact Likelihood Estimation for a
Negative Binomial Regression Model with Missing Outcomes, Biometrics

## Installation

You can install the released version of mreg from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("mreg")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("shug0131/mreg")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE}
library(mreg)
 mod1 <- mreg( damaged~offset(log(intervisit.time))+esr.init,
 data=public,patid=ptno,print.level=1, iterlim=1000 )
 mod1
 summary(mod1)
```



